---
title: "MyProject"
output: html_document
---
```{r eval = TRUE, echo=TRUE, comment=NA, warning=FALSE, message=FALSE,results='markup'}
ProjectData <- read.csv(file = "data/Boats.csv", header = TRUE, sep=",")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Questions

1. Can you find which column asks about the name of the brand rated? 
2. Can you find the average rating to question " `r gsub("_", " ", gsub("\\.", " ", "Q1_3_The.brand.of.boat.I.buy.says.a.lot.about.who.I.am"))` ".
3. Which of the R packages or github repositories you explored did you find interesting?
4. *(Extra)* What is the percentage of male in this population? How many of them responded that they plan to purchase a boat in the future? 
5. Finally, once you answer all questions, please commit-then-push to your github (as shown in steps 3-5 of the [Getting Started Instructions](https://github.com/InseadDataAnalytics/INSEADAnalytics/wiki/Getting-Started) document) your file as well as all other files in the new directory you created.

**Your Answers here:**

1.
```{r eval = TRUE, echo=TRUE, comment=NA, warning=FALSE, message=FALSE,results='markup'}
print(colnames(ProjectData)[53])
```

2.
```{r eval = TRUE, echo=TRUE, comment=NA, warning=FALSE, message=FALSE,results='markup'}
mean(ProjectData[,4])
```

3. tictactoe

4. 

<br>
<br>

<hr>
<hr>
